\section{Implementation of Lind}
\label{sec.implementation}

To test our Lock-in-Pop design, we used it to implement a secure virtual machine
called Lind\footnote{\scriptsize An old English word for a shield constructed from two layers of
linden wood, providing strength in a lightweight form, the name is appropriate for
a virtual machine that adapts two technologies\textendash
yet still protects vulnerable OS kernel code from exploitation by
untrusted user programs.}.
Lock-in-Pop utilizes a
computational module and a library OS. In Lind, Native Client (NaCl) serves as the former,
while Restricted Python (Repy), with a POSIX interface built into it, performs the
task of the latter.
What follows is a brief description of these components and how they were integrated
into Lind, followed by a brief example of how the system works.

\subsection{Primary Components}

\textbf{Native Client.}
We use NaCl to isolate the computation of the user application
from the kernel. NaCl allows Lind to work on most types of legacy code.
It compiles the programs to produce a binary with software fault isolation.
This prevents the majority of applications from performing system calls
or executing arbitrary instructions.
Instead, the application will call into a small privileged
part of the NaCl TCB that forwards system calls, usually to the OS for
processing. To build Lind, we changed the NaCl TCP to
forward these calls to the library OS that we call SafePOSIX (details below).

\textbf{Seattle's Repy.}
To build an API to access the safe parts of the underlying kernel, we need
two things. First, we need a restricted sandbox that isolates computation
and only allows access to commonly used kernel paths.  We used
Seattle's Repy~\cite{Repy-10} sandbox to perform this task.
Second, we chose the widely accepted standard POSIX interface to
provide complex system functions to user programs. However, to enforce isolation,
we needed to modify our POSIX implementation.

\textit{The Repy Sandbox Kernel.}
As the only piece of code in contact with the system call paths of the TCB,
the sandbox kernel's security is of paramount concern.
We used Seattle's Repy system API due to its tiny sandbox kernel
(comprised of around 8K LOC), and its ability to provide straightforward
access to the minimal set of system call API needed to build general
computational functionality. Repy allows
access only to the popular portions of the OS kernel through 33 basic API
functions, including 13 network functions, 6 file functions, 6 threading functions,
and 8 miscellaneous functions (Table \ref{table:RepyKernel}) 
~\cite{Repy-10, RepyKernel}. 
The code is written using style guidelines designed to ease security auditing 
of the code~\cite{style}.

\begin{table}
\centering
\caption {Repy sandbox kernel functions that support Lind's SafePOSIX re-creation.}

  \begin{tabular}{ | p{2.5cm} | p{4.5cm} |}
  \hline
  \textbf{Repy Function} & \textbf{Available System Calls}  \\ \hline

Networking & \emph{gethostbyname, openconnection, getmyip, socket.send, socket.receive, socket.close,
listenforconnection, tcpserversocket.getconnection, tcpserversocket.close, sendmessage, listenformessage,
udpserversocket.getmessage, and udpserversocket.close.} \\ \hline

I/O Operations & \emph{openfile, file.close, file.readat, file.writeat, listfiles, and removefile.} \\ \hline

Threading & \emph{createlock, sleep, lock.acquire, lock.release, createthread, and getthreadname.} \\ \hline

Miscellaneous Functions & \emph{getruntime, randombytes, log, exitall, createvirtualnamespace,
virtualnamespace.evaluate, getresources, and getlasterror.}  \\ \hline
    \end{tabular}
    \label{table:RepyKernel}
\end{table}

The Repy sandbox code provides containment for the SafePOSIX implementation.
Repy has been audited by a professional penetration tester and, since 2010,
the Seattle testbed has operated a bug bounty program for security flaws in the
sandbox~\cite{seattle}.
The code is deployed in daily use across thousands of devices, and has been examined by
hundreds of parties. Despite the discovery of bugs in other parts of the 
system, to date no security flaws have been found in the sandbox
kernel. While there certainly could be bugs in the sandbox kernel, having a 
small, auditable piece of code helps to reduce the risk of such occurrences.

\subsection{Enhanced Safety in Call Handling with SafePOSIX Re-creation}

However, Lind's security does not rely solely on Repy's
safety record.
The kernel interface is extremely rich and hard to protect.
The dual sandbox Lock-in-Pop design used to build Lind provides enhanced
safety protection through both isolation and a POSIX interface that
reformulates risky system calls to
provide sufficient API for legacy applications, with minimal impact on the kernel.

\textbf{An example of system call execution.}
In Lind, a system call issued from user code is
received by NaCl, and then redirected to our system API module, which
includes a POSIX API. This set of standard
operating system interfaces provides
necessary operating functionalities. A standard POSIX API is large and complex,
making it difficult to ensure its implementation is secure and bug-free.
Lind takes advantage of the fact that Repy is a programming language sandbox to
construct a variation on the POSIX API. Following the
Lock-in-Pop design, to service a system call in NaCl, a server routine in
Lind marshals its arguments into a text string, and sends the call and the arguments
to the Repy sandbox. The re-created system call marshals the result and
returns it back to NaCl. Eventually, the result is returned as the appropriate
native type to the calling program.

The file system API in Lock-in-Pop needs only
to provide functionality of writing data to storage.
%\yanyan{why only discuss file system?
%how about network, threading, etc?}
%\yiwen{threading is done by the OS kernel directly, no reconstruction to discuss.
%And our network functions are really simple, things like opening and closing a socket is
%not very exciting.}
It eliminates the need of having a direct abstraction, the
concept of file permissions, links, or even the concept of multiple files.
The system API safe re-creation is a set of more complicated system calls
derived from functions in the sandbox kernel.
It serves as a mediator between the user code
and the OS kernel. The re-creation is safe
because the reconstructed calls are isolated in a sandbox, and its code is written
 in a memory-safe programming language.

Here is an example of how this re-creation would work with the symbolic link function. 
Instead of relying on the underlying kernel to create symbolic links between real files 
in the host file system, Lind builds and maintains its own metadata to represent a virtual symbolic link 
between files within Lind's file system. In this case, if there is a bug in this symbolic link function, 
such as creation of a link with a deleted file, the bug will be contained within Lind's re-creation. 
As a result, instead of creating a security issue, the application is denied privileged access
to the host OS kernel. 
Therefore, attackers will not be able to leverage a bug within the symbolic link function to 
exploit the host kernel.  

The Lind design offers a promising new approach to OS kernel code protection.
 To determine if the ideas behind Lind were valid, we
designed a multi-step study to compare its security performance against a number
 of existing virtualization systems. Details of the study and its results are presented
 in the following section.
